---
title: "Results of the student survey on first-year Phd courses"
author: "Andrea Hofer, Ursina Schaede, Matteo Roberto Greco"
date: "9/27/2017"
output: 
  pdf_document:
    toc: true
    toc_depth: 1
    fig_width: 5.5
    fig_height: 4
---

```{r setup, include=FALSE, message = FALSE, echo = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos = 'h')
```



```{r message = FALSE, echo = FALSE, warning = FALSE}
# This file creates histograms for all the questions in the data set
rm(list = ls())
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
# Load libraries
library(lettercase)
library(ggplot2)
library(tibble)
library(readr)
library(knitr)
library(dplyr)
library(tidyr)
#library(janitor)
```


```{r message = FALSE, echo = FALSE, warning = FALSE}
# Load the data set
fy_df = read.table("./data_raw/fy_eval.csv", header = TRUE, sep = ",", check.names = FALSE, na.strings = c(""," ","NA"), stringsAsFactors = FALSE)


```

```{r message = FALSE, echo = FALSE}
# Clean up data:
read_chunk('clean_data.R')
```
```{r replace_linebreak, echo = FALSE}
```
```{r replace_percentage, echo = FALSE}
```
```{r replace_text, echo = FALSE}
```
```{r fix_column_names, echo = FALSE}
```
```{r correct_column_type, echo = FALSE}
```


```{r echo = FALSE, message = FALSE}
# Function that creates histograms and prints out strings:

create_plot <- function(beginning,end, print = TRUE) {
  for (i in beginning:end) {
    if (is.integer(fy_df[[i]])) {                             # if column is int, create histogram
      if (grepl('%+', names(fy_df)[i])) {                     # if column has % sign, change labels of histogram
       cat("##Statement: ", paste0(names(fy_df)[i]), "  \n")  # print out column name
       histogram = ggplot(data = fy_df) +                     # create histogram
         geom_bar(mapping = aes(x = fy_df[[i]])) +
         labs(x = "Possible answers ranging from 0-25% to 75-100%",
              y = "Count") +
         scale_x_continuous(breaks = c(1, 2, 3, 4), labels = c("0-25%", "25-50%", "50-75%", "75-100%"), limits =                 c(0.5,4.5)) +
         theme_bw()
        print(histogram)
       cat("  \n")
      } else {                                               # if no % sign, have different graph labels
        cat("##Statement: ", paste0(names(fy_df)[i]), "  \n")
        histogram = ggplot(data = fy_df) +
         geom_bar(mapping = aes(x = fy_df[[i]])) +
         labs(x = "Possible answers ranging from 1 (stongly disagree) to 5 (strongly agree)",
              y = "Count") +
         scale_x_continuous(breaks = c(1, 2, 3, 4, 5), limits = c(0.5,5.5)) +
         theme_bw()
       print(histogram)  
       cat("  \n")
      }
    } else {                                                 # if column not integer, print out text in string 
     cat("  \n###", paste0(names(fy_df)[i]), "  \n")         # print out column name
      for (j in 1:15) {
        if (!is.na(fy_df[[j,i]])) {
          cat(" * ", paste(fy_df[[j,i]]), "  \n")
        }
      }
    }
    cat("  \n")
  }
}
```

# General Assessment of the first year courses 2016/2017 
```{r message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(2,33)
```
\pagebreak

#Assessment of the course Macroeconomics for Research Students in Fall 2016 
```{r, message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(34,94)
```
 \pagebreak
 
#Assessment of the course Microeconomics for Research Students in Fall 2016 
```{r, message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(95,139)
```
\pagebreak

#Assessment of the course Econometrics for Research Students in Fall 2016 
```{r, message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(140,178)
```
\pagebreak

#Assessment of the course Macroeconomics for Research Students in Spring 2017 
```{r, message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(179,240)
```
\pagebreak

#Assessment of the course Microeconomics for Research Students in Spring 2017 
```{r, message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(241,280)
```
\pagebreak

#Assessment of the course Econometrics for Research Students in Spring 2017 
```{r, message = FALSE, echo = FALSE, warning = FALSE, results = "asis"}
create_plot(281,328)
```



